DP Problems of Interest

### 2012-10-02 docs/roadmap/problems.tex
problem description precisions

@@

{\color{red}
\item Matrices: $M_{n\times n}, B_{n \times n}$ \textit{<<first edge, last edge>>} upper triangular including main diagonal 
\item Alphabets:\ul
	\item Input: $\Sigma(S_{(i,j)})=\{0..m\}$ with $m=\max_S(i,j) \forall i,j$ determined at runtime\footnote{We need to scan/have stats about $S$ and that's where LMS plays a role}.
	\item Cost matrix: $\Sigma(M)=\{0..z\}$ with $z = m \cdot (n-2)$ (we add at most $n-2$ edges).
	\item Backtrack matrix: $\Sigma(B)=\{stop, 0..n\}$ (the index of the edge we add)
	\ule
\item Initialization: $M_{(i,i)}=0, B_{(i,i)}=stop \quad\forall i$
\item Recurrence: \[M_{(i,j)}=\left\{ \max_{i<k<j}M_{(i,k)}+M_{(k+1,j)} + S(i,k) \,\,\rule[-.75em]{.5pt}{2em}\,\,  k \right\} = B_{(i,j)} \]
	It is interesting to note that even in the sequential world, this problem is best solved 
	by filling the diagonals, ie. computing sub-solutions for all polygons on size $k$ before
	those of size $k+1$.
\item Backtracking: Starting at $B_{(0,n)}$ and let current point you backtrack drawing an edge from the current position to the backtracking position ??

\item Visualisation: in its traditional form the matrix is upper triangular with diagonal excluded.
\begin{center}\setlength{\unitlength}{.6cm}\begin{picture}(8,9)
	\put(-.7,6.5){\rotatebox{90}{First}}\put(-.4,6.4){\linethickness{1pt}\vector(0,-1){2}}
	\put(.2,8.2){Last}\put(1.5,8.4){\linethickness{1pt}\vector(1,0){2}}
	\Cfl{\Cg}\Cfd{\Cz}
	\Cd[0,1]{6,1}{2.8}\Cd[0,1]{6,2}{1.8}\Cd[0,1]{6,3}{0.8}
	\Cd[1,0]{3,4}{2.8}\Cd[1,0]{4,4}{1.8}\Cd[1,0]{5,4}{0.8}
	\put(3.5,4.5){\line(3,-1){3}}
	\put(4.5,4.5){\line(2,-2){2}}
	\put(5.5,4.5){\line(1,-3){1}}
	%\Cd[1,-1]{5,2}{0.8}
\Cm\end{picture}\end{center}

\item Optimizations: XXX we need to rotate that matrix to progress in the same direction as usual, that is towards bottom right.
}
\ole

>>>>

\def\Cmlong{\put(6.5,4.5){\circle*{.4}}\multiput(0,0)(1,0){16}{\line(0,1){8}}\multiput(0,0)(0,1){9}{\line(1,0){15}}} % matrix base
\def\Cfu#1{#1{8,7}#1{9,7}#1{10,7}#1{11,7}#1{12,7}#1{13,7}#1{14,7}#1{9,6}#1{10,6}#1{11,6}#1{12,6}#1{13,6}#1{14,6}#1{10,5}#1{11,5}#1{12,5}#1{13,5}#1{14,5}#1{11,4}#1{12,4}#1{13,4}#1{14,4}#1{12,3}#1{13,3}#1{14,3}#1{13,2}#1{14,2}#1{14,1}} % triangular upper (function)

@@

\item Matrices: $M_{n\times 2n}, B_{n \times 2n}$ \textit{<<first edge, last edge>>} upper triangular including main diagonal 
\item Alphabets:\ul
	\item Input: $\Sigma(S_{(i,j)})=\{0..m\}$ with $m=\max_S(i,j) \forall i,j$ determined at runtime\footnote{We need to scan/have stats about $S$ and that's where LMS plays a role}.
	\item Cost matrix: $\Sigma(M)=\{0..z\}$ with $z = m \cdot (n-2)$ (we add at most $n-2$ edges).
	\item Backtrack matrix: $\Sigma(B)=\{stop, 0..n\}$ (the index of the edge we add)
	\ule
\item Initialization: $M_{(i,i)}=0, M_{(i,i+1)}=0, B_{(i,i)}=stop \quad\forall i$

\item Recurrence: \[M_{(i,j)}=\left\{ \max_{i<k<j}M_{(i,k)}+M_{(k+1,j)} + S(i,k) \,\,\rule[-.75em]{.5pt}{2em}\,\,  k \right\} = B_{(i,j)} \]
	It is interesting to note that even in the sequential world, this problem is solved 
	by filling the diagonals, ie. computing sub-solutions for all polygons of size $k$ before
	those of size $k+1$.

\item Backtracking: Start at $B_{(1,n)}$. Use the following recursive function for the smaller polygons:
	\[{\rm BT}(B_{(i,j)}=k) \mapsto \left\{\begin{array}{ll} A_i & \text{if } k=0 \lor k=j \\
		\Big( {\rm BT}(B_{(i,k)}) \Big) \cdot \Big( {\rm BT}(B_{(k+1,j)}) \Big) & \text{otherwise} \end{array}\right.\]

\item Visualisation: the layout is the a matrix of size $n \times (2n-2)$, because of polygons being 
"cyclical" in nature.
\begin{center}\setlength{\unitlength}{.6cm}\begin{picture}(16,9)
	\put(-.7,6.5){\rotatebox{90}{First}}\put(-.4,6.4){\linethickness{1pt}\vector(0,-1){2}}
	\put(.2,8.2){Last}\put(1.5,8.4){\linethickness{1pt}\vector(1,0){2}}
	\Cfl{\Cg}\Cfd{\Cz}\Cfu{\Cg}
	\Cd[0,1]{6,1}{2.8}\Cd[0,1]{6,2}{1.8}\Cd[0,1]{6,3}{0.8}
	\Cd[1,0]{3,4}{2.8}\Cd[1,0]{4,4}{1.8}\Cd[1,0]{5,4}{0.8}
	\put(3.5,4.5){\line(3,-1){3}}
	\put(4.5,4.5){\line(2,-2){2}}
	\put(5.5,4.5){\line(1,-3){1}}
	%\Cd[1,-1]{5,2}{0.8}
\Cmlong\end{picture}\end{center}

\item Optimizations: we need to rotate that matrix to progress in the same direction as usual, that is towards bottom right.
{\color{red}}
\ole
